Homelessness and Drug Toxicity

### 2024-03-16 paper/paper.qmd
deleted neg binomial model, revised some of the writing

---
title: "Homelessness and Drug Toxicity"
author: 
  - Gavin Crook
  - Samarth Rajani
  - Mohid Sharif
thanks: "Code and data are available at: https://github.com/MohidSharif/Drug-Toxicity-and-Homelessness.."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
header-includes:
 \usepackage{float}
 \floatplacement{figure}{H}
---

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

@@

The goal of our modelling strategy is twofold. Firstly, we use a poisson distribution and a negative binomial distribution as we have count data.Both distribution can be use on count data, and by using both we are able to compare results. Secondly, we use a multilevel or Bayesian model. We use this multilevel model to account for the nested nature of the data. All counts of deaths are nested within a year and then age group and gender. This always the model to control variance within each nested data point.

@@

We expect a their to be a larger relationship between males and the number of deaths. This is because there are more males within the homeless population and more males homeless as a result of addiction to drugs. These reason make it clear that that the male relationship is larger than the female.

@@

Thirdly, we expect changes within years as the death count increased during the pandemic seen in @age-graph. The years pre and post Covid-19 are extremely similar. There was a clear increase during the pandemic but not the topic of this paper, therefor not studied further.

@@

This table is for negative binomial model
```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults2
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

#modelsummary::modelsummary(
#  list(
#    "Gender Only" = fifth_model,
#    "Age Only" = fourth_model,
#    "Age and Gender" = sixth_model
#  ),
#  statistic = "mad",
#  fmt = 2
#)
```

>>>>

---
title: "Homelessness and Drug Toxicity"
author: 
  - Gavin Crook
  - Samarth Rajani
  - Mohid Sharif
thanks: "Code and data are available at: https://github.com/MohidSharif/Drug-Toxicity-and-Homelessness.."
date: today
date-format: long
abstract: "In this study, we investigated fatalities due to drug toxicity among the homeless population over the years, examining trends across age and gender. Fatalities increased steadily from 2017 onwards across all ages and genders until 2021, where we observed a sharp spike in deaths of males aged between 20 and 59 years of age, which returned back to expected pre pandemic levels in 2023. The study highlights the neglected state of the homeless in Toronto, which require targeted interventions to bolster their welfare especially during a public health crisis."
format: pdf
number-sections: true
bibliography: references.bib
header-includes:
 \usepackage{float}
 \floatplacement{figure}{H}
---

@@

@@

The goal of our modelling strategy is twofold. Firstly, we use a poisson distribution and a negative binomial distribution as we have count data. Both distribution can be use on count data, and by using both we are able to compare results. Secondly, we use a multilevel or Bayesian model. We use this multilevel model to account for the nested nature of the data. All counts of deaths are nested within a year and then age group and gender. This allows the model to control variance within each nested data point.

@@

We expect their to be a larger relationship between males and the number of deaths. This is because there are more males within the homeless population and more males homeless as a result of addiction to drugs. These reasons make it clear that that the male relationship is larger than the female.

@@

Thirdly, we expect changes within years as the death count increased during the pandemic seen in @age-graph. The years pre and post Covid-19 are extremely similar. There was a clear increase during the pandemic but not the topic of this paper, therefore not studied further.

@@
